
<style type="text/css">
hide {
  display: none;
}
</style>

```{r setup, child = 'analysis/00-prep.R', include=F, echo=F, eval=F}

```

The whole process can be summarized as follows.

0. Download the reports to a local directory and create a data frame with the year and file location of the report.

  + `paths_info`.

  + I wrote a wrapper function for `download.file()` called `download_report()` to assist with this. This function specified the correct url given a year.

1. Import the raw text for each report to create a singular data frame with nested data frames storing the text for each year's report.

  + `pages_nest`.

  + I used `purrr::map()` and `pdftools::pdf_text()` with `year` as a grouping variable.
  
  + Notably, this data frame has each report stored as a list column named `page`.

```{r pages_nest-1, include=F, echo=F, eval=F}
pages_nest
```

2. "Unnest" the singular data frame to create a "long" data frame where each row represents a page in the reports.

3. Split this long data frame with pages as observations into two data frames, one for the table of contents (TOC) for each report and another for the body of each report.

4. Clean the two data frames (for TOC and body content) separately.

5. Create "child" data frames as needed for analysis.

6. Visualize the most interesting child data frames from the analysis.






2. "Unnest" the `pages_nest` data frame to create the `pages` data frame.

  + Noteably, I added a index `idx_page` (via `dplyr::row_number()`). However, `idx_page` doesn't correspond directly to the page numbers of the reports because the reports have various type of pages leading up to the first numbered page---title page, blank pages, a table of contents, and an exective summary. The numbered pages in each report begin somewhere in the 30s---it varies for each report---in terms of the "raw" PDF page number.
  
  + This `pages` data frame has each page's raw text stored an individual row. Of course, this is quite messy. For example, the second page of the executive summary reads like `"    Executive Summary\r\n    Review of Real-Time Market Outcomes\r\n    Although only a small share [...]"`.

3. Split the `pages` data frame into the the data frames `toc_pages` and `body_pages`, which--in case it isn't obvious--represent the table of contents and body or the report.

4. Do analysis based on the `toc_pages` data frame.

4. Unnest, clean, and augment `toc_pages` data frame, creating the `toc_aug` data frame.

5. Create


99. Create the supplementary data frame `body_rngs` to "map" the page numbers to each report.

  + The data frame `pages_n` is created beforehand to aid with the mapping.


## Analyzing the Table of Contents of Each Report

1. "Munge"`toc_pages`.

  + For this task, I wrote and used a custom function `convert_page_to_lines()` to create the data frame `toc` with rows corresponding to each line of the table of contents sections.

  + These rows look like the following.

```{r toc_ex_show-1, eval=F}
toc_ex
```

  + Note that the `convert_page_to_lines()` function is key to this cleaning step. It uses an idiom that seems like it could be applied to many kinds of text parsing---namely, `stringr::str_split(x, "\\n") %>% purrr::map(stringr::str_squish) %>% unlist() %>% data frame::enframe()`.

2. "Augment" and "clean" the `toc` data frame with columns for `label`, `index` (the , and `page_num`.
  + For example

```{r toc_aug_ex_show-1, eval=F}
toc_aug_ex
```

  + Initially, I had hoped to use an approach like that demonstrated by #rstats aficionado [`hrbrmstr`]() in [this post about parsing pdf tables](https://rud.is/b/2017/01/26/one-view-of-the-impact-of-the-new-immigration-ban-freeing-pdf-data-with-tabulizer/), but I concluded that the data was too "irregular" to warrant this approach. Thus, I turned to every data scientist's/software engineer's best friend---[regular expressions](https://en.wikipedia.org/wiki/Regular_expression)! (Please acknowledge the sarcasm :).) Thankfully, the data was uniform enough to be parsed in this manner.

## Analyzing the Body of the Reports
